---
title: "Codebook"
author: "Yuri-Sh"
date: "Friday, December 19, 2014"
output:
  html_document:
    keep_md: yes
---

Feature Selection 
=================

The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals 
measured during 6 different activities of 30 different subjects.

These time domain signals (prefix 'TimeDomain' to denote time) were captured at a constant rate of 50 Hz. 
Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals using another low pass Butterworth filter with a corner frequency of 0.3 Hz. 

Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals. 
Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm. 

In addition a Fast Fourier Transform (FFT) was applied to some of these signals. 
Note the 'FrequencyDomain' to indicate frequency domain signals. 

The set of variables that were estimated from these signals are: 

 - Mean value (Mean)
 - Standard deviation (STD)
 - Weighted average of the frequency components to obtain a mean frequency (MeanFreq)

The data was in addition post-processed:
for all observations for a given subject and given activity each variable was averaged.

This resulting dataset contains 79 measurements (variables) for each of 6 activities performed by 30 subjects (180 rows).


The notation for the variables is defined by the the following convention:
      <Domain><Type><Measurement/Calculation><Axis/Magnitude><Processing type>

      Domain                    : TimeDomain or FrequencyDomain
      Type                      : Body or Gravity
      Measurement/Calculated    : Acceleration (measured) or AccelerationJerk (calculated) 
                                        or Gyroscope (measured) GyroscopeJerk (calculated) 
      Axis/Magnitude            :  X or Y or Z or Magnitude
      Processing type           : Mean or STD or FreqMean
    
    
The following activities were considered in this data collection:
       - Walking
       - WalkingUpstairs
       - WalkingDownstairs
       - Sitting
       - Standing
       - Laying


```{r echo=FALSE, results='hide',warning=FALSE}
invisible(source("run_analysis.R", verbose=FALSE))
```


```{r echo=FALSE,results='asis',warning=FALSE}
invisible(library(xtable,quietly = TRUE))
conversionDictionary<-data.frame(strippedNames)
colnames(conversionDictionary)<-c("Variable name")
print(xtable(conversionDictionary, align=c('l','c')),type="html")

```



